Writing News Captions with Bags of Attention

### 2019-11-04 paper/paper.tex
Write introduction

%%%%%%%%% ABSTRACT
\begin{abstract}
   We propose an end-to-end model to generate image captions in news articles.
   By combining the transformer architecture, byte-pair encoding, pretrained
   text and image embeddings, and bags of attentions, our system is able to
   describe an image using specific events and names mentioned in the article.
   Our model achieves state-of-the-art results on the existing GoodNews
   dataset. We also extend the GoodNews dataset to improve the quality of
   articles and study the importance of the image location on the page.
\end{abstract}

@@

Our main contributions are as follows:

\begin{itemize}
   \item We show that combining article attention with pre-trained
   contextualized word piece embeddings allows our model to generate captions
   containing relevant words that were not seen during training.

@@

   \item We build on the GoodNews dataset to produce a larger and more
   complete news captioning dataset consisting of 445,828 articles from the New
   York Times and their 794K images with captions. In contrast to GoodNews
   our dataset contains the full article text, and the location of the image
   within the page.
\end{itemize}

@@

Biten \etal~\cite{Biten2019GoodNews} further refined this approach by
developing a two-stage architecture to handle entity names. In the first stage,
the model generates a template with placeholders such as PERSON and
ORGANIZATION. In the second stage, the model finds the best matched sentence in
the article and replace the placeholder with an entity mentioned in that
sentence. They also created the ``GoodNews" dataset, which contains more
samples than MSCOCO \cite{Lin2014MicrosoftCC} and BreakingNews
\cite{Ramisa2016BreakingNewsAA} datasets.

@@

\begin{table*}[t]
	\caption {Model complexity: Number of trainable parameters}
	\label{tab:models}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Parameters \\
      \midrule
      GloVe + LSTM & 137M \\
      GloVe + Transformer & 148M \\
      RoBERTa + LSTM & 139M \\
      RoBERTa + Transformer & 154M \\
        + faces & 171M \\
        + names & 175M \\
        + faces + names & 192M \\
		\bottomrule
	\end{tabular}
\end{table*}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
   We propose an end-to-end model to generate image captions in news articles.
   By combining the transformer architecture, byte-pair encoding, RoBERTa
   embeddings for text, ResNet-152 embeddings for images, and bags of
   attentions, our system is able to describe an image with specific named
   entities mentioned in the article. Our model achieves a CIDEr score of 54 on
   the GoodNews dataset, significantly outperforming the previous state-of-art
   CIDEr of 13. We also introduce the NYTimes+ dataset, an extended version of
   GoodNews with higher-quality articles and metadata that allow us to study
   the importance of the image location within the text. On NYTimes+, we
   achieve a CIDEr of 51. Pretrained models and source code are available from
   \href{https://github.com}{https://anonymized}.
\end{abstract}

@@

Most existing captioning systems can only generate a generic description of an
image \cite{Vinyals2014ShowAT, Fang2014FromCT, Karpathy2015DeepVA,
Rennie2016SelfCriticalST, Lu2016KnowingWT, Anderson2017BottomUpAT}, mainly
because these architectures cannot handle an open vocabulary and early
captioning datasets such as MS COCO \cite{Lin2014MicrosoftCC,
Chen2015MicrosoftCC} and Flickr30k \cite{Young2014FromID} were annotated using
only visual cues present in the image. More recently, datasets such as TIME
\cite{Tariq2017ACE}, BreakingNews \cite{Ramisa2016BreakingNewsAA}, and GoodNews
\cite{Biten2019GoodNews} include real-life captions scraped from online
newspapers. To the best of our knowledge, all of the existing models
that are trained on these news datasets use template-based methods to insert
named entities.

This motivates us to ask whether it is possible to design a fully end-to-end
model for news image captioning. The model would need to 1) attend to
contextual cues from different modalities (image and text) and 2) generate
captions that contain specific information including rare proper names that
have not been seen in the training data. To answer this, we look at the recent
development in sequence-to-sequence architectures and language modeling.

The most successful family of models in natural language understanding and
generation are the transformer networks, which consist of layers of
self-attention and feed-forward connections stacked on top of each other
\cite{Vaswani2017AttentionIA}. Transformers have consistently been shown to
outperform RNN architectures in language modeling \cite{Radford2019LanguageMA},
story generation \cite{Fan2018HierarchicalNS}, summarization
\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.

Furthermore, transformers have led to the rise of unsupervised language
representation learning such as BERT \cite{Devlin2019BERT}, XLM
\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT}. The contextual word
embeddings provided by these methods have helped establish new state-of-the-art
results on many natural language understanding benchmarks including GLUE
\cite{Wang2019GLUE}, SuperGLUE \cite{Wang2019SuperGLUEAS}, and SQuAD
\cite{Rajpurkar2016SQuAD, Rajpurkar2018KnowWY}, even surpassing the human
baselines in many cases.

In parallel to the development of these pre-training methods, many novel
techniques have been proposed to improve training convergence and handle more
diverse data inputs. The most significant contribution is the use of byte-pair
encoding \cite{Sennrich2015NeuralMT} to handle an open vocabulary. This is done
by representing a rare word as a sequence of subword units.

The goal of this paper is to make use of these recent developments, along with
their bags of tricks, to carefully design a captioning system most appropriate
for news images. Our main contributions are thus threefold:

\begin{enumerate}
   \item We show that combining article attention with pre-trained
   contextualized word piece embeddings allows our model to generate captions
   containing relevant words that were not seen during training.

@@

   \item We build on the GoodNews dataset to produce a larger and more complete
   news captioning dataset consisting of 445,828 articles from the New York
   Times and their 794K images with captions. This constitutes the largest
   news image captioning dataset to date. In contrast to GoodNews our dataset
   contains the full article text, and the location of the image within the
   page.
\end{enumerate}

@@

Biten \etal~\cite{Biten2019GoodNews} further refined this approach by
developing a two-stage architecture to handle entity names. In the first stage,
the model generates a template with placeholders such as PERSON and
ORGANIZATION. In the second stage, the model finds the best matched sentence in
the article and replace the placeholder with an entity mentioned in that
sentence. They also created the ``GoodNews" dataset, which contains more
samples than MSCOCO and BreakingNews
\cite{Ramisa2016BreakingNewsAA} datasets.

@@

\begin{table*}[t]
	\caption {Model complexity: Number of trainable parameters}
	\label{tab:models}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Parameters \\
      \midrule
      GloVe + LSTM & 153M \\
      GloVe + Transformer & 148M \\
      RoBERTa + LSTM & 139M \\
      RoBERTa + Transformer & 154M \\
        + faces & 171M \\
        + names & 175M \\
        + faces + names & 192M \\
		\bottomrule
	\end{tabular}
\end{table*}
